Changes after the last submission

### 2021-09-05 paper/changes.tex
Small changes

  In a machine learning based setting, our goal of detecting new changes is a `prediction' problem in a continuous solution space i.e., \textit{``given intensities of a voxel at various time instants in a longitudinal setting, what will be the intensity of the same voxel at the next time instant?''} This estimation can be learnt by a deep neural network only if there are hundreds if not, thousands of time instants at which the previous voxel intensities are known for each voxel. This amount of data is not available to us, and may be hard to acquire because each specimen is usually scanned only a couple of times in any longitudinal study. Further, a specific `event-of-interest' may occur just once in a longitudinal study and hence training on data of all previous time instants may be misleading. If however, we use measurements from identical and full-cycle longitudinal studies (including events-of-interest) of similar specimen (instead of the `same' specimen as we used), a deep-learning technique may be applied. We see this as an extension of using object-prior generated from the same object, and hence we have not explored this direction.

>>>>

  In a machine learning based setting, our goal of detecting new changes is a `prediction' problem in a continuous solution space i.e., \textit{``given intensities of a voxel at various time instants in a longitudinal setting and partial measurements of the voxel at the current time, what will be the intensity of the same voxel at the current time instant?''} This estimation can be learnt by a deep neural network only if there are hundreds if not, thousands of time instants at which the previous voxel intensities are known for each voxel. This amount of data is not available to us, and may be hard to acquire because each specimen is usually scanned only a couple of times in any longitudinal study.

  Further, a specific `event-of-interest' may occur just once in a longitudinal study and hence training on data of all previous time instants may be misleading. If however, we use measurements from identical and full-cycle longitudinal studies (including events-of-interest) of similar specimen (instead of the `same' specimen as we used), a deep-learning technique may be applied. We see this as an extension of using object-prior generated from the same object, and hence we have not explored this direction.
